\chapter{Introduction}\label{ch:introduction}
\fancyhead[LE,RO]{\thechapter\hsp Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}

\begin{quote}
\textit{\enquote{The process of receiving or giving systematic instruction, especially at a school or university}} \cite{EducationDictionaries}
\end{quote}
This is a definition of education. In the western world, including Denmark, school or university is where most people get their education. The majority of people go through at least primary school, and in Denmark many also choose to go to high school, known as the gymnasium \cite{2017FortsatUndervisningsministeriet}. School includes a lot of different entities. It takes teachers, a principal, the parents of the student, and (in Denmark) the state, who finances all levels of education. As such a lot of people are involved in education of students, and therefore a lot of people are interested in the education going well.
\newline\newline
According to the Danish Ministry of Higher Education and Science \cite{MinistryofHigherEducationandScience2018PrinciplesForskningsministeriet} the main goal of the Danish educational system is to \enquote{ensure that all young people acquire knowledge and competencies which will qualify them to take active part in the knowledge society and contribute to its further development}. This means it is important for the Danish government, and by extension Danish society as a whole, that students reach the peak of their potential. Because of this it can be worrying to hear about the problems the schools are facing, with teachers not having enough time to help all students. In the gymnasium the classes are overcrowded which makes it almost impossible for the teacher to give every student the help they need \cite{Romme-Mlby2018GymnasierGymnasieskolen}. 
\newline\newline
This potentially makes the quality of the education the students get, and the experience of going to school, much worse, since students are not able to get the help they need. This worsening in quality of education can be especially problematic for students who are already struggling with school subjects, as they will find it even harder to perform well since teachers will not be able to provide assistance. 
\newline\newline
Additionally research shows that many students struggle with math \cite{MathTeens}. Math is a very important subject, which impacts many aspects of life and is something a lot of students will find useful later in life. Due to its prominence, the main focus of the report will be on the teaching of math to students.
\newline\newline
One way to try to remedy the problems in the classroom is to use online tools. One example is online courses, revolving around the subjects taught in school. Another example of a tool to help the students learn is chatbots, which are already used in a variety of aspects of modern life. Chatbots also exists in the world of education on platforms such as Facebook's Messenger \cite{Messenger} or Discord \cite{DiscordDownloads} as a means to help students with subjects and tasks they struggle with. 
\newline\indent
Providing the teachers with a tool such as a chatbot to help them give the students a better learning experience, without causing extra stress, could be a way to help the teachers with the problems they are facing. This report will take a look at the Danish gymnasiums and some of the problems they are facing, and how chatbots could be a possible solution. 



