\subsubsection{User Integration}

The database will contain information about the different users accessing the chatbot. Users will have to be inserted into the database, using functionality in the chatbot application. Each user will have a username, a password which will be encrypted in the database, first name and last name. There will also be a bit to determine whether or not the user is activated, allowing for administrators to activate and disable users. Each user will be assigned a role and may be assigned a class, and these define the relations the user has to other things in the database. Initially the roles a user can have are student, teacher or system administrator, but it is possible to create more roles later. The role of the user will determine which parts of the application they will have access to. Students will only have access to the chatbot itself. Teachers will be able to view data on the students. The system administrators will be able to create, edit and delete users and material. 
\newline\newline
The reason for designing the application in such a way that different users get access to different features is because normal users with access to edit the system sensitive information only admins have access to could cause them to potentially severely hamstring the chatbots effectiveness by wittingly or unwittingly sabotaging class lists and material. The user to role relation is what is called a one to many relation, meaning each user can have multiple roles. This is done for multiple reasons, firstly so if you want a user to have different kinds of access, you can assign the user the roles needed to give the necessary access. This avoids having to create new roles to in case  it is possible for a teacher to be a system administrator or in case a user is a student in one class, but an assistant teacher in another. This is also in case further roles is added at some point, where you would want a user to have some of the old roles along with the new roles. Each student can only have a relation to one class, seeing as how they can only be in one class, whereas teachers can have relations to many classes. System administrators cannot have relations to any class. 